%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    {\Huge \scshape Mukesh Kumar} \\[-1pt]
    {\large Software Engineer} \\[6pt]

    \small
    \raisebox{-0.1\height}{\faMapMarker}\ Noida, India \quad
    \raisebox{-0.1\height}{\faPhone}\ +91 9211069461 \quad
    \href{mailto:mukesh.dixena2002@gmail.com}{
        \raisebox{-0.1\height}{\faEnvelope}\ \underline{mukesh.dixena2002@gmail.com}
    } \quad
    \href{https://www.linkedin.com/in/mukesh-dixena/}{
        \raisebox{-0.1\height}{\faLinkedin}\ \underline{LinkedIn}
    } \quad
    \href{https://github.com/Mukeshdixena}{
        \raisebox{-0.1\height}{\faGithub}\ \underline{GitHub}
    }
    \vspace{-6pt}
\end{center}




\section{Summary}

Backend engineer experienced in both Java (Spring Boot, JPA, Hibernate) and Node.js (NestJS),
building scalable microservices, secure REST APIs, and distributed systems. Hands-on with
event-driven patterns (Kafka, Pub/Sub), cloud platforms (AWS and GCP), and performance-focused
service design.




%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

    \resumeSubheading
    {FourthPointer Services Pvt. Ltd.}{Jun 2025 -- Present}
    {\textbf{Software Engineer}}{Noida, India}
    \resumeItemListStart
        \resumeItem{Developed backend services for a FinTech platform using \textbf{NestJS}, \textbf{TypeScript}, and \textbf{PostgreSQL}, supporting \textbf{10k+ monthly transactions}.}
        \resumeItem{Built \textbf{60+ REST APIs} with RBAC, API keys, and payment gateway integrations; optimized queries and caching to reduce latency by \textbf{20–25\%}.}
        \resumeItem{Delivered school planner modules in \textbf{Spring Boot}, improving authentication flows and database performance for \textbf{1,000+ users}.}
        \resumeItem{Built microservices using \textbf{Java}, \textbf{Spring Boot}, \textbf{JPA}, and \textbf{Hibernate}, increasing reliability and reducing repeated data-access issues.}
    \resumeItemListEnd


    \resumeSubheading
    {Hyperreality Technologies Pvt. Ltd.}{Jul 2024 -- May 2025}
    {\textbf{Software Engineer}}{Bengaluru, India}
    \resumeItemListStart
        \resumeItem{Engineered backend components for AR/VR workflows using \textbf{Spring Boot}, reducing manual configuration time by \textbf{60\%}.}
        \resumeItem{Developed \textbf{40+ Spring Boot APIs} for asset processing and configuration metadata, improving system stability.}
        \resumeItem{Optimized \textbf{JPA} queries, caching, and service logic to reduce API response times by \textbf{20\%}.}
        \resumeItem{Implemented secure authentication with \textbf{JWT-based RBAC}, reducing unauthorized access by \textbf{90\%+}.}
        \resumeItem{Improved observability with \textbf{Splunk} dashboards and structured logging.}
    \resumeItemListEnd


    \resumeSubheading
    {Siemens Technology \& Services Pvt. Ltd.}{Jul 2023 -- Jun 2024}
    {\textbf{R\&D Intern}}{Bengaluru, India}
    \resumeItemListStart
    
        \resumeItem{Conducted foundational \textbf{WebGPU R\&D}, reviewing \textbf{20+ research papers} and implementing GPU-parallel \textbf{matrix–vector, stencil, and reduction kernels} executing up to \textbf{10M+ threads} for feasibility analysis.}
        
        \resumeItem{Architected a \textbf{topology optimization and FEA simulation prototype} in WebGPU, enabling \textbf{1M–5M element meshes} through custom compute pipelines and optimized memory layouts.}
        
        \resumeItem{Benchmarked WebGPU performance on \textbf{6+ device classes} (integrated GPUs, mid-range laptops, and workstation GPUs), demonstrating up to \textbf{3× faster} execution compared to CPU-based solvers.}
        
        \resumeItem{Collaborated with senior researchers to validate numerical stability, profiling \textbf{memory throughput, occupancy, and thread distribution}, improving solver precision by \textbf{18\%}.}

    \resumeItemListEnd

\resumeSubHeadingListEnd

\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {O.P. Jindal University, Raigarh}{Aug 2020 -- Jul 2024}
      {Bachelor of Technology in Computer Science and Engineering - CGPA:8.55}{Chhattisgarh, India}
  \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Skills}

\begin{tabularx}{\textwidth}{@{}l X@{}}

\textbf{Backend:} &
Java 17, Spring Boot, Spring Data JPA, Hibernate, JAX-RS, Microservices, Node.js, NestJS, REST APIs, Event-Driven Architecture (Kafka, Pub/Sub) \\

\textbf{Cloud \& DevOps:} &
AWS, GCP (BigQuery, Pub/Sub, Cloud Run), Docker, Jenkins, CI/CD, GitHub Actions, Linux, Nginx, Tomcat \\

\textbf{Databases:} &
PostgreSQL, MySQL, MongoDB, SQL \\

\textbf{Frontend:} &
Vue.js, React, HTML, CSS \\

\textbf{Core Competencies:} &
Data Structures, Algorithms, System Design, OOP, Distributed Systems, Design Patterns (Factory, Builder, Strategy), Observability (Splunk, Dynatrace) \\

\textbf{Tools:} &
Git, IntelliJ IDEA, VS Code, Postman, Jira \\

\end{tabularx}


\vspace{-0.5cm}



\vspace{-16pt}
%-----------PROJECTS-----------

\section{Projects}
\vspace{-5pt}
\resumeSubHeadingListStart

\resumeProjectHeading
  {\textbf{Gym Management System} $|$ \emph{Vue 3, NestJS, Prisma ORM, PostgreSQL, JWT, Pinia, Chart.js}}{}
\resumeItemListStart
    \resumeItem{Launched a production-grade gym management platform for a live client, streamlining onboarding, scheduling, and day-to-day operations, resulting in a \textbf{30\% improvement in process efficiency}.}
    \resumeItem{Designed secure authentication flows and \textbf{role-based access controls}, reducing manual administrative workload by \textbf{40\%}.}
    \resumeItem{Built scalable, containerized backend services with real-time analytics dashboards to improve reliability and support data-driven decisions.}
    \resumeItem{\textbf{Links:}
        \href{http://43.205.122.21}{\underline{Live Demo}} $|$
        \href{https://github.com/Mukeshdixena/gym-backend}{\underline{Backend Repo}} $|$
        \href{https://github.com/Mukeshdixena/DailyGymSoftware}{\underline{Frontend Repo}}}
\resumeItemListEnd

\resumeProjectHeading
  {\textbf{Salon Management System} $|$ \emph{Spring Boot, Java 17, Spring Data JPA, PostgreSQL, Spring Security (JWT), Vue 3, Tailwind}}{}
\resumeItemListStart
    \resumeItem{Developed a full-stack salon management platform with a \textbf{Spring Boot} backend handling bookings, services, provider workflows, and customer flows.}
    \resumeItem{Implemented secure authentication and authorization using \textbf{Spring Security + JWT}, ensuring protected and scalable API access.}
    \resumeItem{Built modular backend services with \textbf{Spring Data JPA}, reducing repetitive queries and improving database performance.}
    \resumeItem{Delivered a Vue 3–based Provider Dashboard supporting real-time appointments, schedules, and profile management.}
    \resumeItem{\textbf{Links:}
        \href{https://github.com/Mukeshdixena/backend-salon-management}{\underline{Backend Repo}} $|$
        \href{https://github.com/Mukeshdixena/provider-dashboard}{\underline{Provider Dashboard Repo}} $|$
        \href{https://github.com/Mukeshdixena/customer-web}{\underline{Customer App Repo}}}
\resumeItemListEnd


\resumeProjectHeading
  {\textbf{Room Rectangle Finder} $|$ \emph{Vue 3, Paper.js, Vite, JavaScript (Geometry Algorithms)}}{}
\resumeItemListStart
    \resumeItem{Built an interactive polygon editor allowing users to draw complex room shapes, add holes, and modify vertices with real-time snapping and smoothing.}
    \resumeItem{Deployed a custom computational geometry algorithm to compute the largest inscribed rectangle (axis-aligned or rotated) in concave polygons with interior holes.}
    \resumeItem{Crafted a multi-angle sweep, grid-sampling, and edge-refinement pipeline, achieving \textbf{1–10 ms} runtime on a typical floor plan.}
    \resumeItem{Added export functionality for PNG blueprints and JSON geometry, supporting CAD, architectural design, and space-optimization workflows.}
    \resumeItem{\textbf{Links:}
        \href{https://mukeshdixena.github.io/Polygons-Placement/}{\underline{Live Demo}} $|$
        \href{https://github.com/Mukeshdixena/Polygons-Placement}{\underline{Repository}}}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------
\section{Achievements}
\resumeSubHeadingListStart
\vspace{-4pt}

\begin{tabularx}{\linewidth}{
    @{}X
    @{\hspace{18pt}}
    X
    @{\hspace{18pt}}
    X@{}
}

\textbf{CodeChef} \newline
Solved \textbf{800+} competitive programming problems. \newline
\href{https://www.codechef.com/users/mukeshdixena72}{\underline{Profile Link}}

&

\textbf{HackerRank} \newline
5-star rating in Problem Solving \newline
5-star rating in C++ \newline
\href{https://www.hackerrank.com/profile/mukeshdixena123}{\underline{Profile Link}}

&

\textbf{LeetCode} \newline
Solved \textbf{300+} data structure and algorithm problems. \newline
\href{https://leetcode.com/u/Mukesh_Dixena/}{\underline{Profile Link}}

\\

\end{tabularx}
\resumeSubHeadingListEnd
\vspace{-6pt}



%-----------CERTIFICATIONS---------------

%-----------COURSES-----------
\section{Courses}

\resumeSubHeadingListStart


\item \textbf{DSA (Java) $|$ Apna College}  
Achieved strong proficiency in core data structures and algorithms using Java. Solved 400+ practice questions across arrays, recursion, graphs, DP, and more.  
\href{https://drive.google.com/file/d/1z9xj0OulGSsjx8Zu5mgJnbznzkEY8VFJ/view?usp=sharing}{\textbf{[Certificate]}}

\item \textbf{Web Development Bootcamp $|$ Udemy}  
Gained hands-on experience building 5+ real-world web development projects. Built responsive, user-friendly interfaces as part of the coursework.  
\href{https://drive.google.com/file/d/15pQuyTNfLo1YtafDsDbMQNC0__s-HTu_/view?usp=sharing}{\textbf{[Certificate]}}

\item \textbf{Programming Certifications $|$ CodeChef}  
Completed multiple programming practice tracks in JavaScript, C++, arrays, and problem-solving fundamentals.  
\href{https://www.codechef.com/users/mukeshdixena72/certificates}{\textbf{[Certificates Link]}}



\resumeSubHeadingListEnd


%-----------PERSONAL DETAILS---------------
\section*{Personal Details}
\begin{tabularx}{\linewidth}{@{}l X@{}}
\textbf{Location:} Noida, Uttar Pradesh, India \\
\textbf{Languages:} English, Hindi \\
\textbf{Work Authorization:} Authorized to work in India \\
\textbf{Notice Period:} Immediate \\
\textbf{Relocation:} Open to relocation \\
\end{tabularx}

\end{document}

